|

### 2020-09-14 paper.Rmd
modify output, should now compile to pdf

@@

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\\gamma=3$ (bottom)"}
library(magick)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_frames <- function(pngs) {
  res <- lapply(pngs, image_read)
  res <- do.call("c", res)
  image_append(res)
}

draw_panel <- function(a, b) {
  whitespace <- image_blank(image_info(a)$width, 25, color = "white")
  img <- c(a, whitespace, b)
  image_scale(
    image_append(img, stack = TRUE),
    "800"
  )
}
mouse_grand <- paste0(dir, "mouse_grand_2c-", frames, ".png")
mouse_grand_panel <- draw_frames(mex_grand)
mouse_sage <- paste0(dir, "mouse_sage_2c_gam3-", frames, ".png")
mouse_sage_panel <- draw_frames(mex_sage)

@@

```{r sketches, fig.cap = "Selected frames  of the tour run on the sketches data using the default tour display (top), and using the default sage display (bottom)."}
frames <- c("001", "036", "077", "092")

@@

```{r pdfsense, fig.cap = "Selected frames of the tour run on the pdfsense data using the default tour display (top), and using the sage display with $R=10$ (bottom)"}
frames <- c("001", "051", "078", "092")

>>>>

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\\gamma=3$ (bottom)", out.width="0.9\\textwidth", fig.align="center"}
library(magick)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_frames <- function(pngs) {
  res <- lapply(pngs, image_read)
  res <- do.call("c", res)
  image_append(res)
}

draw_panel <- function(a, b) {
  whitespace <- image_blank(image_info(a)$width, 50, color = "none")
  img <- c(a, whitespace, b)
  image_append(img, stack = TRUE)
}
mouse_grand <- paste0(dir, "mouse_grand_2c-", frames, ".png")
mouse_grand_panel <- draw_frames(mouse_grand)
mouse_sage <- paste0(dir, "mouse_sage_2c_gam3-", frames, ".png")
mouse_sage_panel <- draw_frames(mouse_sage)

@@

@@

```{r sketches, fig.cap = "Selected frames  of the tour run on the sketches data using the default tour display (top), and using the default sage display (bottom).", out.width="0.9\\textwidth", fig.align="center"}
frames <- c("001", "036", "077", "092")

@@

```{r pdfsense, fig.cap = "Selected frames of the tour run on the pdfsense data using the default tour display (top), and using the sage display with $R=10$ (bottom)", fig.align="center", out.width="0.9\\textwidth"}
frames <- c("001", "051", "078", "092")
